My title

### 2023-03-14 outputs/paper/paper.qmd
graphs and data cleaning, except education year

```{r}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.width=6.5, fig.height=2.8) 
# loading in relevant libraries
library(tidyverse)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(readxl)
library(data.table)
library(lubridate)
library(haven)
library(readxl)
library(ggplot2)
### Input data ###
income_race<-read.csv(here::here("outputs/data/race_income.csv"))
income_sex<-read.csv(here::here("outputs/data/sex_income.csv"))
```

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-raceincome
#| fig-cap: "U.S. Income Distribution by Race"

# Make sure the order of the income level is the order we wanted
income_label <- c("LT $1000", "$1000 TO 2999", "$3000 TO 3999", "$4000 TO 4999", "$5000 TO 5999", "$6000 TO 6999", "$7000 TO 7999", "$8000 TO 9999", "$10000 - 14999", "$15000 - 19999", "$20000 - 24999", "$25000 OR MORE")
income_race$income <- 
  factor(income_race$income, 
         levels = income_label)

#generate graph#
ggplot(income_race, aes(x = income, y = the_number_of_people, fill = race)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x = "Income level", y = "Numbers of people", title = "U.S. Income Distribution by Race") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8))

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-raceincome
#| fig-cap: "U.S. Income Distribution by Sex"

# Make sure the order of the income level is the order we wanted
income_label <- c("LT $1000", "$1000 TO 2999", "$3000 TO 3999", "$4000 TO 4999", "$5000 TO 5999", "$6000 TO 6999", "$7000 TO 7999", "$8000 TO 9999", "$10000 - 14999", "$15000 - 19999", "$20000 - 24999", "$25000 OR MORE")
income_sex$income <- 
  factor(income_sex$income, 
         levels = income_label)

#generate graph#
ggplot(income_sex, aes(x = income, y = the_number_of_people, fill = sex)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x = "Income level", y = "Numbers of people", title = "U.S. Income Distribution by Sex") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8))

@@

@@

Our data is of penguins (@fig-bills).

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (@fig-billssssss). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)

```{r}
#| label: fig-billssssss
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it.

# Model

$$
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
$$ {#eq-bayes}

@eq-bayes seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

We can use maths by including latex between dollar signs, for instance $\theta$.

>>>>

```{r}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.width=6.5, fig.height=2.8)

# loading in relevant libraries
library(RColorBrewer)
library(tidyverse)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(readxl)
library(data.table)
library(lubridate)
library(haven)
library(readxl)
library(ggplot2)

### Input data ###
income_data_percentage<-read.csv(here::here("outputs/data/income_3years.csv"))
sex_data<-read.csv(here::here("outputs/data/sex_data.csv"))
race_data<-read.csv(here::here("outputs/data/race_data.csv"))
employee_status_data<-read.csv(here::here("outputs/data/employee_status_data.csv"))
industry_sector_data<-read.csv(here::here("outputs/data/industry_sector_data.csv"))
science_course_data<-read.csv(here::here("outputs/data/science_course_data.csv"))

@@

```{r, fig.height=8}
#| message: false
#| warning: false
#| echo: false
#| label: fig-1
#| fig-cap: "U.S. Income Distribution from 2014 to 2018"

# Make sure the order of the income level is the order we wanted
income_label <- c("LT $1000", "$1000 TO 2999", "$3000 TO 3999", "$4000 TO 4999", "$5000 TO 5999", "$6000 TO 6999", "$7000 TO 7999", "$8000 TO 9999", "$10000 - 14999", "$15000 - 19999", "$20000 - 24999", "$25000 OR MORE")

income_data_percentage$Income <- factor(income_data_percentage$Income, levels = income_label)

# Define color palette with 3 colors
fill_colors <- brewer.pal(n = 3, name = "RdYlBu")

# Generate graph
ggplot(income_data_percentage, aes(x = Income, y = Number, fill = as.factor(Year))) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = fill_colors) +
  labs(x = "Income Level", y = "Total Number of People", title = "U.S. Income Distribution by Year") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%"), y = Number + 10), position = position_stack(vjust = 0.5), size = 2) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8)) +
  ylim(0, 2400)

@@

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-2
#| fig-cap: "U.S. Income Distribution by Sex"

# calculate the percentage of each sex group for each year
sex_data <- sex_data %>% 
  group_by(year) %>% 
  mutate(percentage = 100 * people / sum(people))

# generate graph
ggplot(sex_data, aes(x = year, y = people, 
                                 fill = sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(percentage), "%"), y = people + 5), position = position_dodge(width = 1), size = 3) +
  labs(x = "Year", y = "People", fill = "Sex",title = "sex")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-3
#| fig-cap: "U.S. Income Distribution by Race"

# calculate the percentage of each race group for each year
race_data <- race_data %>% 
  group_by(year) %>% 
  mutate(percentage = 100 * people / sum(people))

# generate graph
ggplot(race_data, aes(x = year, y = people, 
                                 fill = race)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(percentage), "%"), y = people + 5), position = position_dodge(width = 2), size = 3) +
  labs(x = "Year", y = "People", fill = "Race",title = "race")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-4
#| fig-cap: "U.S. Income Distribution by Employee Status"

# calculate the percentage of each employee status group for each year
employee_status_data <- employee_status_data %>% 
  group_by(year) %>% 
  mutate(percentage = 100 * people / sum(people))

# generate graph
ggplot(employee_status_data, aes(x = year, y = people, 
                                 fill = employee_status)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(percentage), "%"), y = people + 5), position = position_dodge(width = 0.9), size = 3) +
  labs(x = "Year", y = "People", fill = "Employee Status",title = "employee status")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-5
#| fig-cap: "U.S. Income Distribution by Industry Sector"

# calculate the percentage of each industry sector group for each year
industry_sector_data <- industry_sector_data %>% 
  group_by(year) %>% 
  mutate(percentage = 100 * people / sum(people))

# generate graph
ggplot(industry_sector_data, aes(x = year, y = people, 
                                 fill = industry_sector)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(percentage), "%"), y = people + 5), position = position_dodge(width = 0.9), size = 3) +
  labs(x = "Year", y = "People", fill = "Industry Sector",title = "industry sector")

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-6
#| fig-cap: "U.S. Income Distribution by College Level Science Courses"

# calculate the percentage of taking college level science courses for each year
science_course_data <- science_course_data %>% 
  group_by(year) %>% 
  mutate(percentage = 100 * people / sum(people))

# generate graph
ggplot(science_course_data, aes(x = year, y = people, 
                                 fill = science_course)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(percentage), "%"), y = people + 5), position = position_dodge(width = 0.9), size = 3) +
  labs(x = "Year", y = "People", fill = "Whether taking science course",title = "Science course")
